Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-08-17 analysis/report/effectiveness_report.Rmd
add any-admitted to report

>>>>

cat("  \n\n")
print(glue("### Any unplanned hospital admission"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("admitted")
print(glue("#### Cox"), "  \n")
print_plots_effects("admitted", "cox")
print(glue("#### PLR, peicewise"), "  \n")
print_plots_effects("admitted", "plr")
print(glue("#### PLR, spline"), "  \n")
print_plots_spline("admitted")
print_plots_cmlinc("admitted")
